---
output: 
  rmarkdown::html_document
---

**The goal of the challenge** is to quantify tumor heterogeneity (how many cell types are present? In which proportion?) accounting for confounding factors.

We assume **D** is a (MxN) methylation matrix composed of methylation value for N samples, at M CpG methylation sites. Each sample is constituted of **K** cell types. We assume the following model: **D = TA**

with **T** an unknown (MxK) matrix of **K** cell type-specific methylation reference profiles (composed of M sites), and **A** an unknown (KxN) proportion matrix composed of **K** cell type proportions for each sample.

Participants have to identify an **estimate of A matrix**, with the correct number of **K** cell types, for each cohort. 


```{r echo=FALSE}
dataset = readRDS("data.rds")
D = dataset$D
metadata = dataset$exp_grp
```

- D is composed of  `r length(names(D))` cohorts named **`r names(D)[[1]]`**, **`r names(D)[[2]]`**, **`r names(D)[[3]]`** and **`r names(D)[[4]]`**

- **`r names(D)[1]`** is composed of `r ncol(D[[1]])` patients and `r nrow(D[[1]])` methylation sites (beta-values), with cell types proportions highly variable between patients.

- **`r names(D)[2]`** is composed of `r ncol(D[[2]])` patients and `r nrow(D[[2]])` methylation sites (beta-values), with cell types proportions lowly variable between patients.

- **`r names(D)[3]`** is composed of `r ncol(D[[3]])` patients and `r nrow(D[[3]])` methylation sites (beta-values), with cell types proportions highly variable between patients.

- **`r names(D)[4]`** is composed of `r ncol(D[[4]])` patients and `r nrow(D[[4]])` methylation sites (beta-values), with cell types proportions lowly variable between patients.

```{r results="verbatim", echo=TRUE}
dim(D[["france"]])
head(D[["france"]][,1:5])
dim(metadata[["france"]])
head(metadata[["france"]])
```


