---
output: 
  rmarkdown::html_document
---

**The goal of the challenge** is to quantify tumor heterogeneity (how many cell types are present? In which proportion?) accounting for confounding factors.

We assume **D** is a (MxN) methylation matrix composed of methylation value for N samples, at M CpG methylation sites. Each sample is constituted of **K** cell types. We assume the following model: **D = TA**

with **T** an unknown (MxK) matrix of **K** cell type-specific methylation reference profiles (composed of M sites), and **A** an unknown (KxN) proportion matrix composed of **K** cell type proportions for each sample.

Participants have to identify an **estimate of A matrix**, with the correct number of **K** cell types, for each cohort. 


```{r echo=FALSE}
dataset = readRDS("data.rds")
```

- dataset is composed of  `r length(names(dataset))` cohorts named **`r names(dataset)[[1]]`**, **`r names(dataset)[[2]]`**

- **`r names(dataset)[1]`** is composed of `r ncol(dataset[[1]])` patients and `r nrow(dataset[[1]])` methylation sites (beta-values), with cell types proportions highly variable between patients.

- **`r names(dataset)[2]`** is composed of `r ncol(dataset[[2]])` patients and `r nrow(dataset[[2]])` methylation sites (beta-values), with cell types proportions lowly variable between patients.


```{r results="verbatim", echo=TRUE}
dim(dataset[["france"]])
head(dataset[["france"]][,1:5])

```


