---
title: "Cancer Heterogeneity Quantification"
subtitle: "Starting kit"
author: "Florent Chuffart & Magali Richard"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: false
---

```{r label="header", echo=FALSE, eval=TRUE}
knitr::opts_chunk$set(collapse=TRUE, comment = "#>", fig.width=9, fig.height=6, eval=TRUE, echo=FALSE, results="hide")
```

# I. Overview

```{r child='overview.Rmd'}
```


```{r child='data.Rmd'}
```







# II. How to participate?

## Where to go? 

The challenge is hosted on the codalab platform: https://competitions.codalab.org/

To participate, you need to:

1- create an acount on the codalab platform

2- subscribe to the *Quantification of tumor heterogeneity* challenge

3- constitute teams (or not) and design a team coordinator on the platform

## How to start?

```{r child='get_starting_kit.Rmd'}
```


```{r child='evaluation.Rmd'}
```











# III. Submission (example)

```{r child='submission_script.Rmd'}
```


```{r}
source("scoring_program/scoring.r")
```



# IV. References 


Methylation data are simulated *in silico*.

[TCGA] Metadata used to generate confounding effects are coming from the TCGA (The cancer genome atlas). 
They were extracted from several cohorts of patients. 
Here are TCGA Study Abbreviations corresponding to each cancer. 
https://gdc.cancer.gov/resources-tcga-users/tcga-code-tables/tcga-study-abbreviations

[Codalab] https://competitions.codalab.org

[R] https://cran.r-project.org

[RStudio] https://www.rstudio.com





```{r, eval=FALSE}
# SUPPLEMENTAL 
## Few words about the dataset 
dataset = readRDS("data.rds")
D = dataset$D


dim(D[["france"]])
head(D[["france"]][,1:5])


```










# Session Information

```{r, results="verbatim"}
sessionInfo()
```


